Genome-wide changes in expression during inflorescence architecture development

### 2015-10-02 ms.Rmd
No actual changes :)

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes:
  \usepackage{graphicx}
  \usepackage[utf8]{inputenc}
  \DeclareUnicodeCharacter{2265}{$\geq$}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
    toc: true
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    number_sections: yes
  rmarkdown::tufte_handout:
    default
bibliography: bib/papersLib.bibtex
---

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes:
  \usepackage{graphicx}
  \usepackage[utf8]{inputenc}
  \DeclareUnicodeCharacter{2265}{$\geq$}
output:
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
    toc: true
  pdf_document:
    fig_caption: yes
    number_sections: yes
  rmarkdown::tufte_handout:
    default
bibliography: bib/papersLib.bibtex
---
